Summary Statistics

### 2017-07-31 Hours.Rmd
analyzed text, added to other files, updated hours

7/27/2017 | 7 | 12:00-7:00 | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
>> __Total Hours: 133.08__

>>>>

7/27/2017 | 7 | 12:00-7:00PM | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
7/28/2017 | 10.5 | 10:30-9:00PM | Continued with textual features
7/29/2017 | 4 | 5:00-9:00PM | Finished working with text, started on the datetime variable 
7/30/2017 | 7 | 2:30-9:30| Finished datetime, finished all exploratory analyses, read articles from meeting with Data Specialist 
>> __Total Hours: 1...__

### 2017-07-31 freq_words.Rmd
analyzed text, added to other files, updated hours

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
library(survminer)
library(tidyverse)
```

@@

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}
```

@@

```{r, echo = FALSE}
titles_freq <- freq_terms(out_english$title)

@@

ggplot(top50, aes(x = word, y = frequency/nrow(out_english))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

@@

```{r, echo = FALSE}
top10 <- titles_freq[1:10,]
out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
prop_contain <- sum(out_english$contain_top10)/nrow(out_english)
```

@@

```{r, echo = FALSE}
out_english %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
survdiff(surv_object~contain_top10, data = out_english)
```

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
plot_surv(KM_top10, data = out_english)
```

@@

```{r, echo = FALSE}
answered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 1)
unanswered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 0)

@@

```{r, echo = FALSE}
out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$word))

prop_contain_u <- sum(out_english$contain_u)/nrow(out_english)
```

@@

```{r, echo = FALSE}
out_english %>%
  group_by(contain_u) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = out_english)
```

```{r, echo = FALSE}
KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
plot_surv(KM_u, data = out_english)
```

@@

```{r, echo = FALSE}
out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$word))

prop_contain_a <- sum(out_english$contain_a)/nrow(out_english)
```

@@

```{r, echo = FALSE}
out_english %>%
  group_by(contain_a) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = out_english)
```

```{r, echo = FALSE}
KM_a <- survfit(surv_object ~ contain_a, data = out_english)
plot_surv(KM_a, data = out_english)
```

@@

out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$word))

prop_contain_u_dev <- sum(out_english$contain_u_dev)/nrow(out_english)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u_dev, data = out_english)

KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
plot_surv(KM_u_dev, data = out_english)
```

@@

out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$word))
prop_contain_a_dev <- sum(out_english$contain_dev_a)/nrow(out_english)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_dev_a, data = out_english)

KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
plot_surv(KM_dev_a, data = out_english)
```

>>>>

library(dplyr)
x <- out %>% 
  tbl_df() %>%
  filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
```

@@

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time (hours)")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time (hours)") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time (hours)", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

@@

```{r, echo = FALSE}
titles_freq <- freq_terms(x$title)

@@

ggplot(top50, aes(x = word, y = frequency/nrow(x))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

@@

```{r, echo = FALSE}
top10 <- titles_freq[1:10,]
x$contain_top10 <- str_detect(as.character(x$title), pattern = or1(names(top10)))
prop_contain <- sum(x$contain_top10)/nrow(x)
```

@@

```{r, echo = FALSE}
x %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
survdiff(surv_object~contain_top10, data = x)
```

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM_top10 <- survfit(surv_object ~ contain_top10, data = x)
plot_surv(KM_top10, data = x)
```

@@

```{r, echo = FALSE}
answered <- x %>%
  tbl_df() %>% 
  filter(answered == 1)

unanswered <- x %>%
  tbl_df() %>% 
  filter(answered == 0)

@@

```{r, echo = FALSE}
x$contain_u <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))

prop_contain_u <- sum(x$contain_u)/nrow(x)
```

@@

```{r, echo = FALSE}
x %>%
  group_by(contain_u) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = x)
```

```{r, echo = FALSE}
KM_u <- survfit(surv_object ~ contain_u, data = x) 
plot_surv(KM_u, data = x)
```

@@

```{r, echo = FALSE}
x$contain_a <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))

prop_contain_a <- sum(x$contain_a)/nrow(x)
```

@@

```{r, echo = FALSE}
x %>%
  group_by(contain_a) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = x)
```

```{r, echo = FALSE}
KM_a <- survfit(surv_object ~ contain_a, data = x)
plot_surv(KM_a, data = x)
```

@@

x$contain_u_dev <- str_detect(as.character(x$title), pattern = or1(unanswered_devices$word))

prop_contain_u_dev <- sum(x$contain_u_dev)/nrow(x)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u_dev, data = x)

KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = x)
plot_surv(KM_u_dev, data = x)
```

@@

x$contain_dev_a <- str_detect(as.character(x$title), pattern = or1(answered_devices$word))
prop_contain_a_dev <- sum(x$contain_dev_a)/nrow(x)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_dev_a, data = x)

KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = x)
plot_surv(KM_dev_a, data = x)
```

### 2017-07-31 summary_stats.Rmd
analyzed text, added to other files, updated hours

```{r, Importing and setting up the data , include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(ggplot2)
library(survival)
library(survminer)
library(epiR)

proportion_answered <- sum(out_english$answered)/nrow(out_english)
```

@@

* `r nrow(out_english)` observations
* `r round(proportion_answered * 100, digits = 2)` % of questions were answered

@@

```{r, time_until_answer, echo = FALSE}
summary <- summary(out_english$time_until_answer)
```

* **minimum:** `r round(min(out_english$time_until_answer), 2)` hrs
* **maximum:** `r round(max(out_english$time_until_answer), 2)` hrs
* **mean:** `r round(mean(out_english$time_until_answer), 2)` hrs
* **median:** `r round(median(out_english$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs

```{r, distribution of response, echo = FALSE}
ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)") +
  ggtitle("Distribution of time_until_answer values")
```

@@

##### Survival Time Statistics based off of KM Estimator 
```{r, survival analysis statistics, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")

@@

* **Min survival probability:** `r round(min(s$surv), 2)`
* **Max survival probability:** `r round(max(s$surv), 2)`
* **rmean survival time:** `r round(s$table[5], 2)` hrs
* **SE of rmean:** `r round(s$table[6], 2)` hrs
* **Median survival time:** `r round(s$table[7], 2)` hrs
* **95% confidence interval for the median:** (`r round(s$table[8], 2)`,`r round(s$table[9], 2)`)

@@

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
round(quant[[1]], 3)
```
* **Interpretations:**
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)

@@

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = out_english, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
ggsurvplot(KM, data = out_english, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

@@

```{r, cumulative hazard, echo = FALSE}
#KM estimator of cumulative hazard 
fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
fit$H.hat <- -log(fit$surv)

>>>>

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
x <- out %>% 
  tbl_df() %>%
  filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(ggplot2)
library(survival)
library(epiR)
library(survminer)

proportion_answered <- sum(x$answered)/nrow(x)
```

@@

* `r nrow(x)` observations
* `r round(proportion_answered * 100, digits = 2)` % of questions were answered

@@

```{r, echo = FALSE}
summary <- summary(x$time_until_answer)
```

* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
* **maximum:** `r round(max(x$time_until_answer), 2)` hrs, `r round(max(x$time_until_answer)/24, 2)` days
* **mean:** `r round(mean(x$time_until_answer), 2)` hrs, `r round(mean(x$time_until_answer)/24, 2)` days
* **median:** `r round(median(x$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs, `r round(summary[5]/24, 2)` days
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs, `r round((summary[5] - summary[2])/24, 2)` days
* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions had been answered
* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions had been answered

```{r, echo = FALSE}
ggplot(x, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)") +
  ggtitle("Distribution of time_until_answer values")
```

@@

##### Survival Time Statistics based off of KM Estimator 
```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")

@@

* **Min survival probability:** `r round(min(s$surv), 2)`
* **Max survival probability:** `r round(max(s$surv), 2)`
* **rmean survival time:** `r round(s$table[5], 2)` hrs, `r round(s$table[5]/24, 2)` days
* **SE of rmean:** `r round(s$table[6], 2)` hrs
* **Median survival time:** `r round(s$table[7], 2)` hrs
* **95% confidence interval for the median:** (`r round(s$table[8], 2)`,`r round(s$table[9], 2)`)

@@

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
round(quant[[1]], 3)
```
* **Interpretations:**
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
    + highest quantile that exists: `r round(quant$quantile[6], 2)` hrs 64% of the questions have been answered

@@

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

##### Reversing the survival curves

* at 100 hrs, the probability that a question is answered starts to level out at around ~0.63

```{r, echo = FALSE}
reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
ggplot(reversed, aes(x = time, y = prob_ans)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
  scale_y_continuous("Probability a question is answered") + 
  ggtitle("Probability a question is answered vs. time (hours)")
```

@@

```{r, echo = FALSE}
#KM estimator of cumulative hazard 
fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
fit$H.hat <- -log(fit$surv)
